---
title: "Flights"
author: "issa fall"
date: "December 19, 2015"
output: html_document
---
##NYC flights
```{r loading,echo=TRUE}
library(nycflights13)
library(plyr)
library(dplyr)
library(tidyr)
data(flights)
head(flights)
```
##A subset of the rows of the data frame
```{r subset,echo=TRUE}
filter(flights, month == 1, day == 1)
flights %>%
  filter(dep_delay < 10)
flights %>%
  filter(arr_delay < dep_delay)
flights %>%
  filter(hour < 12, arr_delay <= 0)
```
##Arrange:reorder a data frame
```{r reorder,echo=TRUE}
flights %>%
  filter(hour < 8)%>%
  arrange(year, month, day)
flights %>%
  arrange(desc(dep_delay))
```
##Select:select certain columns from a data frame
```{r select,echo=TRUE}
select(flights, year, month, day)
select(flights, year : day)
select(flights, -(year : day))
```
##Mutate:modify or create columns based on others columns
```{r mutate,echo=TRUE}
d<-flights %>%
  mutate(
    gain = arr_delay - dep_delay,
    speed = distance / air_time *60
  )%>%
  filter(gain > 0)%>%
  arrange(desc(speed))
d%>%
  select(year, month, day, dest, gain, speed)
```
##Summarise:collapse a data frame into on row ...
```{r summarise,echo=TRUE}
summarise(flights, delay = mean(dep_delay, na.rm = TRUE))
flights %>%
  filter(dep_delay > 0)%>%
  summarise(arr_delay = mean(arr_delay, na.rm = TRUE))
```
##Group_by:group observations by one or more variable
```{r group_by,echo=TRUE}
flights %>%
  group_by(tailnum)%>%
  summarise(
    count = n(),
    dist = mean(distance, na.rm = TRUE),
    delay = mean(arr_delay, na.rm = TRUE)
  )%>%
  filter(is.finite(delay))%>%
  arrange(desc(count))
flights %>%
  group_by(dest)%>%
  summarise(
    planes = n_distinct(tailnum),
    flights = n()
  )%>%
  arrange(desc(flights))
  
  
