---
title: "movies"
author: "issa fall"
date: "November 21, 2015"
output: html_document
---

##Movies
```{r,echo=TRUE}
library(datasets)
library(plyr)
library(dplyr)
library(reshape2)
library(ggplot2)
data("movies")
head(movies)
str(movies)
movies_df<-tbl_df(movies)
head(movies_df)
movies_with_budget<-filter(movies_df, !is.na(budget))
head(movies_with_budget)
head(filter(movies, Documentary == 1))
head(filter(movies, Documentary == 1)%>%nrow())
good_comedies<-filter(movies, rating > 9, Comedy == 1)
dim(good_comedies)
```
##Let's say we only want highly rated comedies,which a lot of people have watched after year 2000
```{r,echo=TRUE}
movies%>%
  filter(rating > 8, Comedy == 1, votes > 100, year > 2000)
```
##Use of mutate()
##mutate(data, new_col = function(oldcol))
```{r mutate,echo=TRUE}
movies_with_budget<-filter(movies_df, !is.na(budget))
head(movies_with_budget)
mutate(movies_with_budget, costPerMinute = budget/length)%>%
  select(title, costPerMinute)
```
##Use of group_by() & summarize()
##group_by(data, column_to_group)%>%
##summarize(function_of_variable)
```{r,echo=TRUE}
by_rating<-group_by(movies_df, rating)
by_rating%>%summarize(n())
avg_rating_by_year<-group_by(movies_df, year)%>%
  summarize(avg_rating_by_year = mean(rating))
head(avg_rating_by_year)
```
##Chaining the verbs together
##let's put it all together in logical fashion,use a sequence of
##steps to find the most expensive movies per minute of eventual footage
```{r,echo=TRUE}
producer_nightmare<-filter(movies_df, !is.na(budget))%>%
  mutate(costPerMinute = budget/length)%>%
  arrange(desc(costPerMinute))%>%
  select(title, costPerMinute)
head(producer_nightmare,20)
```
##The output of a series of "pipes" can also be fed to a "plot"command
```{r plot,echo=TRUE}
movies%>%
  group_by(rating)%>%
  summarize(n())%>%
  plot()
movies%>%
  group_by(year)%>%
  summarize(y=mean(rating))%>%
  with(barplot(y,names.arg=year,main="AVG IMDB Rating by year"))
```





