---
title: "run_analysis"
author: "issa fall"
date: "December 23, 2015"
output: html_document
        
---
##Code Book
```{r,echo=TRUE}
dir("C:/Users/ndeye amy fall/Desktop/Rstudio/UCI HAR Dataset")
library(dplyr)
library(plyr)
library(tidyr)
library(reshape2)
files<-list.files("UCI HAR Dataset")
files
files[5]
```
##Appending the files
```{r,echo=TRUE}
list.files("UCI HAR Dataset")
files_full<-list.files("UCI HAR Dataset",full.names = TRUE)
files_full
files_full[1]
con<-file("UCI HAR Dataset/activity_labels.txt","rt")
activity_labels<-read.table(con)
head(activity_labels)
str(activity_labels)
con2<-file("UCI HAR Dataset/features.txt","rt")
features<-read.table(con2)
head(features)
str(features)
con4<-file("UCI HAR Dataset/features_info.txt","rt")
features_info<-readLines(con4)
head(features_info)
```
##Appending the files and using split-apply-combine(SAC) method for data frames
```{r,echo=TRUE}

list.files("UCI HAR Dataset/test")
list.files("UCI HAR Dataset/train")
list.files("UCI HAR Dataset/inertial Signals")
files_full_train<-list.files("UCI HAR Dataset/train",full.names = TRUE)
files_full_train
files_full_test<-list.files("UCI HAR Dataset/test",full.names = TRUE)
files_full_test
files_full_inertial<-list.files("UCI HAR Dataset/inertial Signals",full.names = TRUE)
files_full_inertial
con1<-read.table(files_full_inertial[1])
head(con1,10)
con3<-read.table(files_full_test[2])
head(con3)



